---
title: "Basic reactivity"
author: "Howard Baek"
date: "11/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 3.3.6 Exercises

1.

```{r}
server1 <- function(input, output, server) {
  input$greeting <- renderText(paste0("Hello ", name))
}
```

- `input$greeting` is wrong. It should be `output$greeting`
- Inside `renderText`, it should be `input$name` instead of just `name`
- Here is the fix:  `output$greeting <- renderText(paste0("Hello ", input$name))`


```{r}
server2 <- function(input, output, server) {
  greeting <- paste0("Hello ", input$name)
  output$greeting <- renderText(greeting)
}
```

- You can make `greeting` a reactive by adding `reactive()`. Here is the fix: `greeting <- reactive(paste0("Hello ", input$name))`
- Now that `greeting` is a reactive, you need to add parenthesis around it. Here is the fix: `output$greeting <- renderText(greeting())`

```{r}
server3 <- function(input, output, server) {
  output$greting <- paste0("Hello", input$name)
}
```

- Spelling error. We were missing a letter. 
- We are also missing `renderText()`
- Here is the fix: `output$greeting <- renderText(paste0("Hello ", input$name))`


2. I will defer to https://mastering-shiny-solutions.org/basic-reactivity.html#solution-15

3. 

- I think this code will fail because of df[[input$var]]. This expression will fail. 
- They are bad names for a reactive because they are built-in R functions. When you use `range()` or `var()`, other readers won't know if you are using a reactive or a built-in R function. 




